Only the store can save you now:\\updates and vulnerabilities on Android

### 2015-04-02 securityupdates.tex
Remove spurious words from Acknowledgements

\identifying{
\section*{Acknowledgements}
Thanks to Richard Clayton, the mobile security reading group and Anil Madhavapeddy for reading drafts.
Thanks to David Robertson for advice on statistical analysis.
Thanks to Laurent Simon, Thomas Coudray, Adrian Taylor, Justin Case, Giant Pune and Khilan Gudka for reporting vulnerabilities in Android.
This work was partly funded by the EPSRC and Google but the the work presented here does not necessarily reflect their views.
}

>>>>

\identifying{
\section*{Acknowledgements}
Thanks to: Richard Clayton, the mobile security reading group and Anil Madhavapeddy for reading drafts;
David Robertson for statistical advice;
and Laurent Simon, Thomas Coudray, Adrian Taylor, Justin Case, Giant Pune and Khilan Gudka for reporting vulnerabilities.
We were funded by the EPSRC and Google but the the work presented here does not necessarily reflect their views.
}
